---
title: "HW11"
author: "Dandong Tu"
date: "2017/11/29"
output: pdf_document
---

##8.2
###8.2.1
```{r}
library(alr4)
plot(sqrt(stopping$Distance)~stopping$Speed)
```
From the plot we see that the sqrt seems a appropriate transformation for **Distance** that can linearize this regression.

###8.2.2
```{r}
invTranPlot(stopping$Speed,stopping$Distance,-1)
invTranPlot(stopping$Speed,stopping$Distance,0)
invTranPlot(stopping$Speed,stopping$Distance,1)
```
From the plots, it seems none of the value (-1,0,1) are adequate.

###8.2.3
```{r}
invTranPlot(stopping$Speed,stopping$Distance,2)
```
In the graph, the lines fit well. It seems that using lambda = 2 to transform the predictor **Speed**in problem 8.2.2 does match the data well.

###8.8.4
```{r}
w=(1/stopping$Speed)^2
m1=lm(Distance~Speed+I(Speed^2),data=stopping,weights = w)
plot(Distance~Speed,data = stopping)
lines(4:40,predict(m1,data.frame(Speed=4:40)),lty=1,lwd=1)
m11=lm(sqrt(Distance)~Speed,data = stopping)
lines(4:40,predict(m11,data.frame(Speed=4:40))^2,lty=2,lwd=2)
```
\par
From the result, we observed that two lines are very closed and seems like lapped. The reason behind this is that take the sqrt for the **Distance** is same as take **I(Speed^2)**

##8.6
###8.6.1
```{r}
Len=factor(Wool$len,ordered=FALSE)
Amp=factor(Wool$amp,ordered = FALSE)
Load=factor(Wool$load,ordered=FALSE)
Wool2=data.frame(Len,Amp,Load,Wool$cycles)
scatterplotMatrix(~Len+Amp+Load+Wool.cycles,data = Wool2)
```
\par
The scatterplot matrix shows the relations between **Len**,**Amp**,**Load** and **cycles**

###8.6.2
```{r}
m2=lm(Wool$cycles~Len+Amp+Load+Len:Load+Len:Amp+Amp:Load)
summary(m2)
```
\par
The $R^2$ is 0.9952 indicates the models explain 99.52% variability of the response data. Several low p-vale indicates the regressors are statisticlly significant, and the above model describes the data well.
```{r}
print(plot(effect("Amp:Load",m2,),multiline = TRUE))
print(plot(effect("Len:Amp",m2,),multiline = TRUE))
```
\par
The effect plot shows the effect of **AMP** in mean response in different **Len** values.

###8.6.3
```{r}
m3=lm(Wool$cycles~Len+Amp+Load)
summary(m3)
```
\par
The summary shows that the model is not adequate for these data.
```{r}
m4=lm(cycles~len+amp+load,data=Wool)
(inverseResponsePlot(m4))
```
\par
The inverseResponsePlot shows -0.06 is the best fit lambda, the value is pretty closed to 0. 
```{r}
summary(powerTransform(m4))
```
\par
The Lwr bnd to Upr Bnd is incloude value of 0. The powerTransform summary shows that the p-value for lambda=0 is large, so that we are unable to reject the null(lambda=0 which means use log transformation). 

```{r}
boxCox(m4)
```
\par
The Box Cox graph shows that based on a 95% confidence intervial, the lambda value of 0 is inculded. It suggests that use **Log** transformation is appropriate.

###8.6.4
```{r}
m5=lm(log(Wool$cycles)~Len+Amp+Load+Len:Amp+Len:Load+Amp:Load)
m6=lm(log(Wool$cycles)~Len+Amp+Load)
anova(m6,m5)
```
\par
From the result of F-test, p-value is **0.1325** we do not have enough evidence to reject the **H0**, so we use the model **m6** without the interation.
```{r}
print(plot(effect("Len:Amp",m6,),multiline = TRUE))
```
\par
We observed three parallel lines.

```{r}
m7=lm(Wool$cycles~Len+Amp+Load)
print(plot(effect("Len:Amp",m7,),multiline = TRUE))
```
\par
Now comparing the result with 8.6.2, we have the similar graphs. 


